Model Recognition as Planning

### 2019-03-10 doc/icaps-19/camera-ready/model-recognition.tex
ICAPS19: intro example changed

As an example of model recognition, imagine a robot in a $N\times N$ grid whose navigation is determined by the \strips\ model of Figure~\ref{fig:model-example}. According to this model, when {\tt\small $q0$} ({\tt\small $q1$}) holds, the robot is at an even (odd) row and can move right (left) by incrementing (decrementing) its x-coordinate. Other models that shape different strategies of robot navigation can be defined within the same state variables altering the way {\tt\small $q0$} and {\tt\small $q1$} are required and updated. Given the partially observed plan execution of Figure~\ref{fig:grid-example}, where variables {\small\tt $q0$} and {\small\tt $q1$} are unobserved, model recognition aims to identify the robot action schemata that explains this observation.

@@

We show the effectiveness of our approach in three experiments that encode a set of different \strips\ models.
The first experiment is a proof-of-concept \emph{classification task} that perfectly recognizes the regular automata of a given string. Additionally, the two assumptions underpinning our formal theory are experimentally proved in the second experiment by varying the degree of observability. Finally, the robustness of the approach is shown in the third experiment where actions and intermediates states are unobservable. A significant lesson from the experiments is that our approach allows us to predict behaviours that are not ruled by a goal-driven deliberative planning model (e.g., models of fixed programs or finite state machines --regular automata-).

>>>>

%As an example, imagine you are given a set of navigation policies for a $N\times N$ grid. Figure~\ref{fig:model-example} shows an example of such policy, according to which, the agent can only move right when he is at an even row ({\tt\small $q0$} holds), and left when he is at an odd row ({\tt\small $q1$} holds). Other models that shape different strategies of robot navigation can be defined within the same state variables altering the way {\tt\small $q0$} and {\tt\small $q1$} are required and updated. Given the partially observed plan execution of Figure~\ref{fig:grid-example}, where variables {\small\tt $q0$} and {\small\tt $q1$} are unobserved, model recognition aims to identify the navigation policy that better explains this observation.

As an example, imagine you are given a set of models, each one encoding a different navigation policy for a $N\times N$ grid. Figure~\ref{fig:model-example} shows an example of one such model, according to which, the agent can only move right when he is at an even row ({\tt\small $q0$} holds), and left when he is at an odd row ({\tt\small $q1$} holds). Given the partially observed plan execution of Figure~\ref{fig:grid-example}, where variables {\small\tt $q0$} and {\small\tt $q1$} are unobserved, model recognition aims to identify the navigation policy (model) that better explains this observation.

%As an example of model recognition, imagine a robot in a $N\times N$ grid whose navigation is determined by the \strips\ model of Figure~\ref{fig:model-example}. According to this model, when {\tt\small $q0$} ({\tt\small $q1$}) holds, the robot is at an even (odd) row and can move right (left) by incrementing (decrementing) its x-coordinate. Other models that shape different strategies of robot navigation can be defined within the same state variables altering the way {\tt\small $q0$} and {\tt\small $q1$} are required and updated. Given the partially observed plan execution of Figure~\ref{fig:grid-example}, where variables {\small\tt $q0$} and {\small\tt $q1$} are unobserved, model recognition aims to identify the robot action schemata that explains this observation.

@@

We show the effectiveness of our approach in three experiments that encode a set of different \strips\ models.
The first experiment is a proof-of-concept \emph{classification task} that perfectly recognizes the regular automata of a given string. The second experiment, where the number of trajectories explaining the observation is bounded, shows that a more accurate model prediction is achieved with more complete observations. Finally, the robustness of the approach is shown in the third experiment where actions and intermediates states are unobservable. A significant lesson from the experiments is that our approach allows us to predict behaviours that are not ruled by a goal-driven deliberative planning model (e.g., models of fixed programs or finite state machines --regular automata-).
